Open source landscape ecology tools

### 2020-07-20 paper/paper.Rmd
adds new code for rev deps

The most prominent package allowing for raster data representation is *raster*.
<!-- maybe check number of reverse dependencies? -->
A *raster* successor aimed at the simpler interface and improved performance, *terra*, is now being developed, however, it could take several years for this package to be adopted by users.
Alternatively, *stars* package can be used to read and process raster data.
<!-- stars -->

The *sp* package was a standard for vector data representation for more than 10 years.
<!-- used by many packages -->
However, it is now in a maintenance mode only with a recommended successor - the *sf* package.
<!-- terra new vector representations -->
<!-- maybe check number of reverse dependencies? -->

>>>>

The most prominent package allowing for raster data representation is *raster*.
A *raster* successor aimed at the simpler interface and improved performance, *terra*, is now being developed, however, it could take several years for this package to be adopted by users.
Alternatively, *stars* package can be used to read and process raster data.
It is interconnected with the *sf* package, and beside raster support, it provides tools for spatial data cubes.

The *sp* package was a standard for vector data representation for more than 10 years.
As of 2020, more than 500 R packages directly depends or imports *sp*.
However, it is now in a maintenance mode only with a recommended successor - the *sf* package.
<!-- terra new vector representations -->
